The French Covid-19 vaccination policy did not solve vaccination inequities: a nationwide longitudinal study on 64.5 million individuals

### 2022-07-04 ms/figs.Rmd
format supp table

>>>>

# Format in wide format
#  Initialize output table
supptab <- data.frame(predictor = sort(unique(tmp$predictor)))
supptab$`class of predictor` <- NA
for(thedate in dates){
  supptab[, thedate] <- NA
}
prefixORcol <- "OR_(signif)_" # Prefix of the OR columns
names(supptab)[2 + seq_along(dates)] <- paste0(prefixORcol, names(supptab)[2 + seq_along(dates)])

# For each line, i.e. for each predictor
for(i in seq_len(nrow(supptab))){
  # Subset of the data for this predictor
  sub <- tmp[tmp$predictor == supptab[i, "predictor"], ]
  supptab[i, "class of predictor"] <- unique(sub$`class of predictor`) # Add info on predictor class

  # Add info on OR at specific dates
  for(j in 1:length(dates)){
    thedate <- dates[j]
    subb <- sub[sub$date == thedate, ] # Subset of the data for this date
    signif <- ifelse(subb$significant, "*", "-") # Sign for significativity 
    supptab[i, paste0(prefixORcol, thedate)] <- paste0(subb$OR, " (", signif, ")")
  }
}

# Remove "X" at start of name
iX <- which(substr(supptab$predictor, 1, 1) == "X") # Lines with "X"
supptab[iX, "predictor"] <- vapply(supptab[iX, "predictor"], FUN = function(x) substr(x, 2, nchar(x)), FUN.VALUE = "x") # Remove "X" on these lines

supptab

# Save as csv
write.csv(supptab, file = "../ms/SuppTable_OR_wide.csv", row.names = FALSE)
